---
title: "GHC Demo Assignment"
subtitle: "CSC 110 - Fall 2025"
author: "Muhammad Ahmad Adil"
date: "October 12, 2025"
format:
  html:
    toc: true
    toc-depth: 2
    theme: solar
  pdf: default
---

```{r}
#| include: false

library(tidyverse)
```

# Homework

hello

```{r}
#| fig-cap: "Figure 1"

ggplot(mpg, aes(x = displ, y = hwy)) +
  geom_point(color = "blue") +
  labs(
    title = "Engine Displacement vs. Highway Fuel Efficiency",
    x = "Engine Size (Liters)",
    y = "Highway MPG"
  )
```

[Visit Davidson College](https://www.davidson.edu)

### My Other Classes
- Data Science & Society  
- Intro to Accounting
- American Economic History  
- Medieval Philosophy

### My Top 3 Favorite Movies / TV Shows
1. Brookly Nine Nine
2. The Dark Knight
3. Prison Break

Here’s a small footnote for fun.[^1]  

[^1]: This is a Markdown footnote example.  

$$
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$

```{mermaid}
flowchart LR
  A[Hard edge] --> B(Round edge)
  B --> C{Decision}
  C --> D[Result one]
  C --> E[Result two]
```

Homework

{{< pagebreak >}}

Reflection

> "Four score and seven years ago our fathers brought forth on this continent, a new nation, conceived in Liberty, and dedicated to the proposition that all men are created equal."

::: {.callout-note}
Note that I am using three types of callouts
:::

::: {.callout-tip}
Right now I am using tip
:::

::: {.callout-important collapse="true"}
Now I am trying to make important collapsible
:::

# Reflection

### 1. Using Quarto themes

One technique I found really helpful was learning how to change Quarto **themes**. In the final project I can use this to add a unique and good looking theme to my liking which will go with our topic and overall project.

### 2. Displaying Equations

I also learned how to write **mathematical equations** directly inside Markdown using  `$$`. This feature helps me clearly show any formulas and steps I might use in the final project showing any calculations I do using the data.

### 3. Callout Blocks

Finally, I enjoyed experimenting with **callout blocks** which let me highlight key notes, tips, and important messages in a visually appealing way. They are perfect for separating important reminders or summaries from all the data and analysis I have in the final project. The collapsible option is especially useful when presenting long explanations that I want to hide otherwise.